Temperature and wave exposure as drivers of morphology in two kelp species

### 2019-07-16 paper_morph_new.Rmd
update ecklonia deep wave plots

pos_lam_temp <- c("Cool temperate", "Warm temperate")

@@

  scale_x_discrete(limits = pos_lam_temp) + 

@@

```{r ecklonia  processing, message=FALSE, warning=FALSE, include=FALSE}

library(ggplot2)

@@

eck_deep <- eck_data %>% 
  filter(population == "Deep")

# custom positions for wave exposure categories and sites
pos_exposure <- c("Fully sheltered", "Extremely sheltered", "Very sheltered", "Sheltered", "Moderatley exposed", "Exposed", "Very exposed")
pos_eck<- c("Betty's Bay", "Kalk Bay", "A-Frame",  "Miller's Point", "Baboon Rock", "Batsata Rock", "Buffelsbaai", "Scarborough", "Soetwater","Kommetjie","Hout Bay", "Oudekraal", "St Helena Bay")

frond_mass_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = frond_mass, fill = wave_exposure)) +
         scale_x_discrete(limits = pos_exposure) + 
         geom_boxplot(outlier.shape = NA) 
primary_length_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = primary_length, fill = wave_exposure)) +
         scale_x_discrete(limits = pos_exposure) + 
         geom_boxplot(outlier.shape = NA) 
primary_width_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = primary_width, fill = wave_exposure)) +
         scale_x_discrete(limits = pos_exposure) + 
         geom_boxplot(outlier.shape = NA) 
frond_length_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = frond_length, fill = wave_exposure)) +
         scale_x_discrete(limits = pos_exposure) + 
         geom_boxplot(outlier.shape = NA) 
stipe_mass_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = stipe_mass, fill = wave_exposure)) +
         scale_x_discrete(limits = pos_exposure) + 
         geom_boxplot(outlier.shape = NA) 
stipe_length_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = stipe_length, fill = wave_exposure)) +
         scale_x_discrete(limits = pos_exposure) + 
         geom_boxplot(outlier.shape = NA) 
stipe_circ_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = stipe_circ, fill = wave_exposure)) +
         scale_x_discrete(limits = pos_exposure) + 
         geom_boxplot(outlier.shape = NA) 
tufts_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = tufts, fill = wave_exposure)) +
         scale_x_discrete(limits = pos_exposure) + 
         geom_boxplot(outlier.shape = NA) 
epi_length_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = epi_length, fill = wave_exposure)) +
         scale_x_discrete(limits = pos_exposure) + 
         geom_boxplot(outlier.shape = NA) 
total_length_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = total_length, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure) + 
  geom_boxplot(outlier.shape = NA) +
  ylim(0, 2000)

@@

grid.arrange(frond_mass_plot,primary_length_plot,primary_width_plot,frond_length_plot,stipe_mass_plot,stipe_length_plot,stipe_circ_plot, tufts_plot, epi_length_plot,total_length_plot, ncol = 3, nrow = 4)

>>>>

pos_temp <- c("Cool temperate", "Warm temperate")

@@

  scale_x_discrete(limits = pos_temp) + 

@@

```{r ecklonia  processing, message=FALSE, warning=FALSE, include=FALSE}
library(ggplot2)

@@

eck_deep <- eck_data %>% 
  filter(population == "Deep")
eck_shall <- eck_data %>% 
  filter(population == "Shallow")

eck_deep$wave_exposure <- factor(eck_deep$wave_exposure, levels=c("Fully sheltered", "Extremely sheltered", "Very sheltered","Moderately exposed", "Exposed", "Very exposed"), labels=c("Fully sheltered", "Extremely sheltered", "Very sheltered","Moderately exposed", "Exposed", "Very exposed"))

# custom positions for wave exposure categories and sites
pos_exposure <- c("Fully sheltered", "Extremely sheltered", "Very sheltered","Moderately exposed", "Exposed", "Very exposed")

frond_mass_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = frond_mass, fill = wave_exposure)) +
         scale_x_discrete(limits = pos_exposure) + 
         geom_boxplot(outlier.shape = NA)  + 
  ylab("Frond mass (g)") +
primary_length_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = primary_length, fill = wave_exposure)) +
         scale_x_discrete(limits = pos_exposure) + 
         geom_boxplot(outlier.shape = NA)  + 
  ylab("Primary length (cm)") +
primary_width_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = primary_width, fill = wave_exposure)) +
         scale_x_discrete(limits = pos_exposure) + 
         geom_boxplot(outlier.shape = NA)  + 
  ylab("Primary width (cm)") +
frond_length_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = frond_length, fill = wave_exposure)) +
         scale_x_discrete(limits = pos_exposure) + 
         geom_boxplot(outlier.shape = NA)  + 
  ylab("Frond length (cm)") +
stipe_mass_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = stipe_mass, fill = wave_exposure)) +
         scale_x_discrete(limits = pos_exposure) + 
         geom_boxplot(outlier.shape = NA)  + 
stipe_length_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = stipe_length, fill = wave_exposure)) +
         scale_x_discrete(limits = pos_exposure) + 
         geom_boxplot(outlier.shape = NA)  + 
stipe_circ_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = stipe_circ, fill = wave_exposure)) +
         scale_x_discrete(limits = pos_exposure) + 
         geom_boxplot(outlier.shape = NA)  + 
  ylab("Stipe circumference (cm)") +
tufts_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = tufts, fill = wave_exposure)) +
         scale_x_discrete(limits = pos_exposure) + 
         geom_boxplot(outlier.shape = NA)  + 
  ylab("No of Tufts") +
epi_length_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = epi_length, fill = wave_exposure)) +
         scale_x_discrete(limits = pos_exposure) + 
         geom_boxplot(outlier.shape = NA)  + 
  ylab("Epi length (cm)") +
total_length_plot <- ggplot(data = eck_deep, aes(x = wave_exposure, y = total_length, fill = wave_exposure)) +
  scale_x_discrete(limits = pos_exposure) + 

@@

ggarrange(frond_mass_plot,primary_length_plot,primary_width_plot,frond_length_plot,stipe_mass_plot,stipe_length_plot,stipe_circ_plot, tufts_plot, epi_length_plot,total_length_plot, labels = "AUTO", common.legend = TRUE, legend = "bottom")
